Enforced Invariant Confluence

### 2017-01-30 doc/paper/alie.tex
Explained that i-replayability isn't good enough.

This is an unfortunate result. It says that for a set of transactions $T$ and
invariant $I$, if \liconfluence{} does not imply \iconfluence{}, then all our
efforts to determine \liconfluence{} are for naught. However, for some
transactions $T$ and invariants $I$, \liconfluence{} is equivalent to
\iconfluence{}! When this is the case, we can check whether $T$ is
\iconfluent{} with respect to $I$ by checking if it is \liconfluent{} with
respect to $I$.

So when is \liconfluence{} equivalent to \iconfluence{}? Well, look at $D$,
$D_a$, $D_b$, and $D_d$ in \figref{iconfluence-example}. If there existed some
\imp{} transaction chain $B$ such that $D \circ B = D_d$ and $I(B@D)$, then we
could remove the split and merge created by $D_a$ and $D_b$ and replace it with
the chain $B$ from $D$ to $D_d$. This is shown in \figref{mergeremoved}. For
simplicity, we've assumed $B = c_1, c_2, c_3$. Now that \figref{mergeremoved}
doesn't contain any intermediate merges, \liconfluence{} is equivalent to
\iconfluence{}.

@@

\todo{Figure out how hard it is to determine \ireplayability{}. I think the
Collatz conjecture can be reduced to it, but I haven't worked out the kinks.}

>>>>

This is an unfortunate result. It says that for a set of transactions $T$ and
invariant $I$, if \liconfluence{} does not imply \iconfluence{}, then all our
efforts to determine \liconfluence{} are for naught. However, not all hope is
lost. Perhaps for some transactions $T$ and invariants $I$, \liconfluence{} is
equivalent to \iconfluence{}. When this is the case, we can check whether $T$
is \iconfluent{} with respect to $I$ by checking if it is \liconfluent{} with
respect to $I$.

\subsection{\ireplayability{}}
So when is \liconfluence{} equivalent to \iconfluence{}? Let's take a look at a
\emph{wrong} first guess.

Look at $D$, $D_a$, $D_b$, and $D_d$ in \figref{iconfluence-example}. If there
existed some \imp{} transaction chain $B$ such that $D \circ B = D_d$ and
$I(B@D)$, then we could remove the split and merge created by $D_a$ and $D_b$
and replace it with the chain $B$ from $D$ to $D_d$. This is shown in
\figref{mergeremoved}. For simplicity, we've assumed $B = c_1, c_2, c_3$. Now
that \figref{mergeremoved} doesn't contain any intermediate merges,
\liconfluence{} is equivalent to \iconfluence{}.

@@

Unfortunately, this line of reasoning is wrong. Consider the state diagram
shown in \figref{ireplayability-notgoodenough}. Here, we can't use
\ireplayability{} to reduce the diagram to a simple diamond.

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[yscale=1.2]
    \inode[]{a}{ 1, 5};
    \inode[]{b}{ 0, 4};
    \inode[]{c}{ 2, 4};
    \inode[]{d}{ 0, 3};
    \inode[]{e}{ 2, 3};
    \inode[]{f}{ 0, 2};
    \dnode[]{g}{ 2, 1};
    \foreach \x/\y in {a/b, a/c, b/d, c/d, c/e, d/f, e/g, f/g} {
      \draw[txn] (\x) -- (\y);
    }
  \end{tikzpicture}
  \caption{A state diagram illustrating the inadequacy of \ireplayability{}.}
  \label{fig:ireplayability-notgoodenough}
\end{figure}

\begin{itemize}
  \item \todo{%
    Figure out if \ireplayability{} can be used to determine \iconfluence{}.
  }
  \item \todo{%
    Figure out how hard it is to determine \ireplayability{}. I think the
    Collatz conjecture can be reduced to it, but I haven't worked out the
    kinks.
  }
\end{itemize}
